Dynein project log

### 2016-08-03 thesis_stuff/thesis_stuff.tex
Add a bit to the CLT derivation.

\begin{align}
  F{P(t_0+1,x')} &= F{\int_{-\infty}^{\infty}W(x'-x)P(t_0,x)dx}\\
  \tilde{P(t_0+1,k)} &= N\tilde{W(k)}\tilde{P(t_0,k)}\\
\end{align}

We now let our initial time $t_0$ be zero and note that, because
$W_n(\delta x) = W(\delta x)^n$, we can simplify our expression to:

\begin{align}
  \tilde{P(n,k)} &= N\tilde{W(k)}^n\tilde{P(t_0,k)}\\
\end{align}

@@

\begin{align}
  P(n,x) &= \int_{-\infty}^{\infty}\tilde{P(n,k)}e^{2\pi ikx}dk
  = N\int_{-\infty}^{\infty}\tilde{W(k)}^n\tilde{P(t_0,k)}e^{2\pi ikx}dk\\
\end{align}

Since $P(0,x)$ is a delta function, we know that $\tilde{P}(0,x) = 1$, so:

\begin{align}
  P(n,x) &=  N\int_{-\infty}^{\infty}\tilde{W(k)}^ne^{2\pi ikx}dk\\
\end{align}

>>>>

\begin{align}
  F\{P(t_0+1,x')\} &= F\left\{\int_{-\infty}^{\infty}W(x'-x)P(t_0,x)dx\right\}\\
  \widetilde{P}(t_0+1,k) &= \widetilde{W}(k)\widetilde{P}(t_0,k)\\
\end{align}

We now let our initial time $t_0$ be zero and note that, because
$W_n(\Delta x) = W(\Delta x)^n$, we can simplify our expression to:

\begin{align}
  \widetilde{P}(n,k) &= \widetilde{W}(k)^n\widetilde{P}(t_0,k)\\
\end{align}

@@

\begin{align}
  P(n,x) &= \int_{-\infty}^{\infty}\widetilde{P}(n,k)e^{2\pi ikx}dk
  = \int_{-\infty}^{\infty}\widetilde{W}(k)^n\widetilde{P}(t_0,k)e^{2\pi ikx}dk\\
\end{align}

Since $P(0,x)$ is a delta function, we know that $\widetilde{P}(0,x) = 1$, so:

\begin{align}
  P(n,x) &=  \int_{-\infty}^{\infty}\widetilde{W}(k)^ne^{2\pi ikx}dk\\
\end{align}

%% The Taylor Series for $\widetilde{W}(k)$ is:

%% \begin{align*}
%%   \widetilde{W}(k) &= \widetilde{W}(0) + k\widetilde{W_1}(0) + \frac{k^2}{2}\widetilde{W_2}(0) + \frac{k^3}{6}\widetilde{W_2}(0)\\
%%   &= 1 + \frac{k^2}{2}\widetilde{W_2}(0)\\
%% \end{align*}

%% \textbf{Because W(k) is an even Gaussian function, $W'(0)$ = 0 and $W(0) = 1$} - is this right?\\

We then make the substitution $\widetilde{W}(k) = \widetilde{C}-1$, so we can use the Binomial Expansion:

\begin{align}
  P(n,x) &=  \int_{-\infty}^{\infty}\left(1 + \widetilde{c}\right)^ne^{2\pi ikx}dk\\
  &= \int_{-\infty}^{\infty}\left(\sum_{\alpha=0}^n {}_nC_\alpha \widetilde{C}^\alpha\right)e^{2\pi ikx}dk\\
  &= \int_{-\infty}^{\infty}\left(\sum_{\alpha=0}^n \frac{n!}{(n-\alpha)!\alpha!} \widetilde{C}^\alpha\right)e^{2\pi ikx}dk\\
\end{align}

The Taylor Series of our goal, the Gaussian function, is:\\

\begin{align*}
  e^{\frac{-x^2}{2\sigma^2}} &= \sum_{\alpha=0}^\infty \frac{(-1)^\alpha}{\alpha!}\left(\frac{x}{\sqrt{2}\sigma}\right)^{2\alpha}\\
\end{align*}

We want to make our expression for $P(n,x)$ resemble this. We begin by saying that, for sufficiently large $n$, the higher-order
$\alpha$ terms in the sum go to zero due to the $1/\alpha!$. Thus, we can extend our sum to infinity:\\

\begin{align}
  P(n,x) &= \int_{-\infty}^{\infty}\left(\sum_{\alpha=0}^\infty \frac{1}{\alpha!}\frac{n!}{(n-\alpha)!} \widetilde{C}^\alpha\right)e^{2\pi ikx}dk\\
\end{align}

We then apply Sterling's Approximation in the form $Z! = e^{Z\ln(Z)-Z}$:

\begin{align}
  P(n,x) &= \int_{-\infty}^{\infty}\left(\sum_{\alpha=0}^\infty \frac{1}{\alpha!}\frac{e^{n\ln(n)-n}}{e^{(n-\alpha)\ln(n-\alpha)-(n-\alpha)}} \widetilde{C}^\alpha\right)e^{2\pi ikx}dk\\
  &= \int_{-\infty}^{\infty}\left(\sum_{\alpha=0}^\infty \frac{1}{\alpha!}\frac{n^ne^{-n}}{(n-\alpha)^{n-\alpha}e^{\alpha-n}} \widetilde{C}^\alpha\right)e^{2\pi ikx}dk\\
\end{align}

Because n is large, we can get rid of its decaying exponentials and simplify:\\

\begin{align}
  P(n,x) &= \int_{-\infty}^{\infty}\left(\sum_{\alpha=0}^\infty \frac{1}{\alpha!}\frac{n^n}{(n-\alpha)^{n-\alpha}e^{\alpha}} \widetilde{C}^\alpha\right)e^{2\pi ikx}dk\\
  &= \int_{-\infty}^{\infty}\left(\sum_{\alpha=0}^\infty \frac{1}{\alpha!}\frac{n^n}{(n-\alpha)^{n-\alpha}} \sqrt{\frac{\widetilde{C}}{e}}^{2\alpha}\right)e^{2\pi ikx}dk\\
\end{align}
